The Strucplot Framework:\\ Visualizing Multi-way Contingency Tables with \pkg{vcd}

### 2005-11-02 trunk/vcd/paper/statreport22.Rnw
report added
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/vcd@493 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\documentclass[article]{jss}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% declarations for jss.cls %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\usepackage{thumbpdf}

%% almost as usual
\author{David Meyer\\Wirtschaftsuniversit\"at Wien \And 
        Achim Zeileis\\Wirtschaftsuniversit\"at Wien \And 
        Kurt Hornik\\Wirtschaftsuniversit\"at Wien}
\title{The Strucplot Framework:\\ Visualizing Multi-way Contingency
  Tables with \pkg{vcd}}

%% for pretty printing and a nice hypersummary also set:
\Plainauthor{David Meyer, Achim Zeileis, Kurt Hornik} %% comma-separated
\Shorttitle{The Strucplot Framework} %% a short title (if necessary)

%% an abstract and keywords
\Abstract{
This paper describes the `strucplot' framework for the visualization of
multi-way contingency tables. Strucplot displays include hierarchical
conditional plots such as mosaic, association, and sieve plots, and
can be combined into more complex, specialized plots for visualizing
conditional independence, GLMs, and the results of
independence tests. The framework's modular design allows
flexible customization of the plots' graphical appearance, including 
shading, labeling, spacing, and legend, by means of \underline{gr}aphical
\underline{ap}pearance \underline{con}trol (`grapcon') functions. 
The framework is provided by the \proglang{R} package \pkg{vcd}.
}

\Keywords{contingency tables, mosaic plots, association plots, sieve plots, 
categorical data, independence, conditional independence, HSV, HCL,
residual-based shading, \pkg{grid}, \proglang{R}}
\Plainkeywords{contingency tables, mosaic plots, association plots,
  sieve plots, categorical data, independence, 
  conditional independence, HSV, HCL, residual-based shading, grid, R}

@@

%% publication information
%% NOTE: This needs to filled out ONLY IF THE PAPER WAS ACCEPTED.
%% If it was not (yet) accepted, leave them commented.
%% \Volume{13}
%% \Issue{9}
%% \Month{September}
%% \Year{2004}
%% \Submitdate{2004-09-29}
%% \Acceptdate{2004-09-29}

%% The address of (at least) one author should be given
%% in the following format:
\Address{
  David Meyer\\
  Department of Information Systems and Process Management\\
  E-mail: \email{David.Meyer@wu-wien.ac.at}\\
  URL: \url{http://wi.wu-wien.ac.at/~meyer/}\\

  Achim Zeileis\\
  Department of Statistics and Mathematics\\
  E-mail: \email{Achim.Zeileis@wu-wien.ac.at}\\
  URL: \url{http://www.ci.tuwien.ac.at/~zeileis/}\\

  Kurt Hornik\\
  Department of Statistics and Mathematics\\
  E-mail: \email{Kurt.Hornik@wu-wien.ac.at}\\
  URL: \url{http://www.wu-wien.ac.at/cstat/hornik/}\\

  Wirtschaftsuniversit\"at Wien\\
  Augasse 2--6
  1090 Wien, Austria\\
}
%% It is also possible to add a telephone and fax number
%% before the e-mail in the following format:
%% Telephone: +43/1/31336-5053
%% Fax: +43/1/31336-734

%% for those who use Sweave please include the following line (with % symbols):
%% need no \usepackage{Sweave.sty}

@@

@@

%% end of declarations %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%% include your article here, just as usual
%% Note that you should use the \pkg{}, \proglang{} and \code{} commands.

\section[Introduction]{Introduction}
%% Note: If there is markup in \(sub)section, then it has to be escape as above.

>>>>

\documentclass[notitle]{Z}

\usepackage{thumbpdf}
\usepackage{statreport}

\title{The Strucplot Framework:\\ Visualizing Multi-way Contingency
  Tables with \pkg{vcd}}

\author{
  David Meyer \And Achim Zeileis \And Kurt Hornik
  \\
  Wirtschaftsuniversit\"at Wien
  }

@@

%% need no \usepackage{Sweave.sty}

@@

\Plainauthor{David Meyer, Achim Zeileis, Kurt Hornik}

\Abstract{
This paper describes the `strucplot' framework for the visualization of
multi-way contingency tables. Strucplot displays include hierarchical
conditional plots such as mosaic, association, and sieve plots, and
can be combined into more complex, specialized plots for visualizing
conditional independence, GLMs, and the results of
independence tests. The framework's modular design allows
flexible customization of the plots' graphical appearance, including 
shading, labeling, spacing, and legend, by means of \underline{gr}aphical
\underline{ap}pearance \underline{con}trol (`grapcon') functions. 
The framework is provided by the \proglang{R} package \pkg{vcd}.
}

\Keywords{contingency tables, mosaic plots, association plots, sieve plots, 
categorical data, independence, conditional independence, HSV, HCL,
residual-based shading, \texttt{grid}, \textsf{R}}

\sloppy{}

@@

@@

\fronttitle{The Strucplot Framework:\\ Visualizing Multi-way Contingency
  Tables with \pkg{vcd}}
\frontauthor{David Meyer, Achim Zeileis, Kurt Hornik}
\frontnumber{22}
\frontdate{November 2005}
\frontpage

\maketitle
